---
title: "Introduction"
include-in-header: 
  - text: |
      <style>
        body {
          text-align: justify;
        }
        h1.title {
          text-align: center;
          padding-top: 20px;
        }

        /* Make plot outputs fill more width */
        .cell-output-display {
          max-width: 100% !important;
        }

        /* Optionally remove left/right padding */
        main.content {
          padding-left: 2rem;
          padding-right: 2rem;
        }
        .nav-buttons {
          display: flex;
          justify-content: space-between;
          margin: 2rem auto;
          max-width: 1000px;
        }
        
        .fade-in-plot {
          opacity: 0;
          transform: translateY(30px);
          transition: opacity 1s ease-out, transform 1s ease-out;
        }
        
        .fade-in-plot.visible {
          opacity: 1;
          transform: translateY(0);
        }

      </style>
format:
  html:
    theme: default
    page-layout: full
toc: false
---


## Shailender/Paul

<!-- Button 1 -->
<button id="show-plot-btn-1" class="btn btn-primary" style="margin-bottom: 1rem;">
  Efficacy of ICI in MCC
</button>

<!-- Plot 1 (initially hidden) -->
<div id="hidden-plot-1" class="fade-in-plot" style="display: none;">

```{r}
#| echo: false
#| warning: false
#| message: false
source(here::here("scripts/Efficacy of ICI in MCC.R"))


mcc_systemic_1L_avg_gt 

```

</div>

<!-- Button 2 --> 

<button id="show-plot-btn-2" class="btn btn-primary" style="margin: 2rem 0 1rem;"> 
   Efficacy of ICI in MCC By N 
</button> 

<!-- Plot 2 (initially hidden) --> 
<div id="hidden-plot-2" class="fade-in-plot" style="display: none;"> 

```{r} 
#| echo: false 
#| warning: false 
#| message: false 
source(here::here("scripts/Efficacy of ICI in MCC.R")) 
mcc_systemic_1L_n_gt 
``` 

</div> 

<!-- Navigation Button --> 
<div class="nav-buttons"> <a href="../Table_1/" class="btn btn-primary">Next →</a> 

</div> 

<!-- JavaScript to handle scroll and click -->


<script>
  document.addEventListener("DOMContentLoaded", () => {
    // Scroll-based fade-in
    const observer = new IntersectionObserver((entries) => {
      entries.forEach(entry => {
        if (entry.isIntersecting) {
          entry.target.classList.add("visible");
        }
      });
    }, { threshold: 0.1 });

    document.querySelectorAll('.fade-in-plot').forEach(el => observer.observe(el));

    // Click-to-show functionality
    document.getElementById('show-plot-btn-1').addEventListener('click', function () {
      document.getElementById('hidden-plot-1').style.display = 'block';
      this.style.display = 'none';
    });

    document.getElementById('show-plot-btn-2').addEventListener('click', function () {
      document.getElementById('hidden-plot-2').style.display = 'block';
      this.style.display = 'none';
    });
  });
</script>

